Dynamic Load Balancing for\\Heterogeneous Systems

### 2011-11-29 paper/paper.tex
Added basic APU section to paper

\subsection{APU Architecture}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut
enim ad minim veniam, quis nostrud exercitation ullamco laboris
nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor
in reprehenderit in voluptate velit esse cillum dolore eu fugiat
nulla pariatur. Excepteur sint occaecat cupidatat non proident,
sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

\subsection{APU Architecture}
The APU is a relatively new, novel architecture that attempts to 
improve on the the discrete CPU+GPU system.  The CPU die is split
between the typical CPU processor as well as allocating space
for a SIMD engine, the basis for a GPU processor.  The APU has a 
shared memory between the CPU and SIMD engine, in which accesses
are facilitated through a high-speed memory controller.  The AMD
Fusion technology is an example of this type of architecture~\cite{AMDFusion}.

One of the main benefits of the APU is the elimination of the PCI-e
bus, which allows for much faster transfer between CPU and GPU.  Daga et al.
show that the AMD Fusion architecture allows for much faster data transfers
between CPU and GPU, allowing for an overall improvement in runtime, despite
reduced compute power on the GPU~\cite{Daga2011}.
